\documentclass[11pt,a4paper]{article}

\usepackage[utf8]{inputenc}
\usepackage{libertine}
%\usepackage[default]{sourcesanspro}
%\usepackage[scaled]{berasans}
%\renewcommand*\familydefault{\sfdefault}
%\renewcommand*\oldstylenums[1]{{\fontfamily{fxlj}\selectfont #1}}
\usepackage[T1]{fontenc}
\usepackage{etaremune}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{array}
\usepackage{setspace}
\usepackage[margin=1in]{geometry}
\usepackage{lastpage}
\usepackage{fancyhdr}
\usepackage{enumitem}
\usepackage{amsmath,amssymb}

\setlength{\parindent}{0cm}
\definecolor{lapislazuli}{rgb}{0.15, 0.38, 0.61}
\newcommand{\selected}{\textcolor{lapislazuli}{\footnotesize $\blacktriangleright$}}

% Use hyperref to allow for interal and external linking
\usepackage[pdftex]{hyperref}
\hypersetup {
    bookmarks=true,                    % show bookmarks bar in pdf reader
    pdftitle={Gregory A. Feiden: Publications},                   
    pdfauthor={Gregory A. Feiden},     % set pdf author
    pdfsubject={Academic Publications of Gregory A. Feiden}, % pdf subject
    colorlinks=true,                   % false = box link, true = colored links
    linkcolor=black,                   % color of internal links
    citecolor=blue,                    % color of citations
    urlcolor=lapislazuli                      % external url color
}
\urlstyle{same}

\newcommand{\email}{gregory.feiden@physics.uu.se}

\markboth{}{\sc Publications by Gregory A. Feiden}
\pagestyle{fancy}

\fancyhead[L]{Gregory A. Feiden -- Personal Number -- Publications}
\fancyhead[R]{\thepage\ of\ \pageref{LastPage}}
\fancyfoot[C]{}
\renewcommand{\headrulewidth}{0.0pt}

\fancypagestyle{plain}{
    \fancyhf{}
    \fancyfoot[C]{\thepage\ of\ \pageref{LastPage}}
    \renewcommand{\headrulewidth}{0.0pt}
    \renewcommand{\footrulewidth}{0.0pt}
}


\begin{document}

%\thispagestyle{plain}

% Name and header
%{\Huge \noindent\textsc{Gregory A. Feiden} \hspace{\fill} {\Large\it Publications}} \\
%\hrule\vspace{\baselineskip}
\onehalfspacing


\noindent {\bf \large 0. Summary}
%
\begin{center}
	18 peer-reviewed publications | 8 lead-author | 380+ citations | {\it h}-index = 11 | $i$10 = 11 
\end{center}

\noindent{\bf \large 1. Peer-reviewed original articles} %\hspace{\fill} {\small $^{\dagger}$ indicates student} \vspace{0.5\baselineskip}

\begin{etaremune}[leftmargin=0.4in]

	\item[{\bf 2016}]

	\item[* 17] \emph{Magnetic Inhibition of Convection and the Fundamental Properties of Low--Mass Stars. III. A Consistent 10 Myr Age for the Upper Scorpius OB Association} \\
		{\bf Feiden, G.~A.} \\
		Astronomy \& Astrophysics, accepted: Mar 2016. \\
		11 pp. --- \href{http://}{LINK}
	
	\item[{\bf 2015}]
	
	\item \emph{How to Constrain Your M Dwarf: Measuring Effective Temperature, Bolometric Luminosity, Mass, and Radius} \\
		Mann, A.~W.; {\bf Feiden, G.~A.}; Gaidos, E.; Boyajian, T.; \& von Braun, K. \\
		2015, The Astrophysical Journal, 804, 64. \\
		38 pp. --- 26 citations --- \href{http://adsabs.harvard.edu/abs/2015ApJ...804...64M}{LINK}
		
	\item \emph{Kepler-445, Kepler-446, and the Occurrence of Compact Multiples Orbiting Mid-M Dwarf Stars} \\
		Muirhead, P.~S.; Mann, A.~W.; Vanderburg, A.; Morton, T.~D.; Kraus, A.; Ireland, M.; Swift, J.~J.; {\bf Feiden, G.~A.}; Gaidos, E.; \& Gazak, J.~Z. \\ 
		2015, The Astrophysical Journal, 801, 18. \\
		15 pp. --- 7 citations --- \href{http://adsabs.harvard.edu/abs/2015ApJ...801...18M}{LINK}
	
	\item \emph{Stellar Diameters and Temperature VI. High angular resolution measurements of the transiting exoplanet host stars HD~189733 and HD~209458 and implications for models of cool dwarfs} \\
		Boyajian, T.~S., von Braun, K., {\bf Feiden, G.~A.}, Huber, D.; Basu, S.; Demarque, P.; Fischer, D.~A.; Schaefer, G.; Mann, A.~W.; White, T.~R.; Maestro, V.; Brewer, J.; Lamell, C.~B.; Spada, F.; L\'{o}pez-Morales, M.; Ireland, M.; Farrington, C.; van Belle, G.~T.; Kane, S.~R.; Jones, J.; ten Brummelaar, T.~A.; Ciardi, D.~R.; McAlister, H.~A.; Ridgway, S.; Goldfinger, P.~J.; Turner, N.~H.; \& Sturmann, L. \\
		2015, Monthly Notices of the Royal Astronomical Society, 447, 846. \\
		12 pp. --- 6 citations --- \href{http://adsabs.harvard.edu/abs/2015MNRAS.447..846B}{LINK}

	\item[{\bf 2014}]

	\item {\it The G+M Eclipsing Binary V530 Orionis: A Stringent Test of Magnetic Stellar Evolution Models for Low--Mass Stars} \\
		Torres, G.; Lacy, C.~H.~S.; Pavlovski, K.; {\bf Feiden, G.~A.}; Sabby, J.~A.; Bruntt, H.; \& Clausen,~J.~V.	\\
 		2014, The Astrophysical Journal, 797, 31. \\
		16 pp. --- 4 citations --- \href{http://adsabs.harvard.edu/abs/2014ApJ...797...31T}{LINK}

	\item {\it Revised age for CM Draconis and WD 1633+572: Toward a resolution of model--observation radius discrepancies} \\
        {\bf Feiden, G.~A.} \& Chaboyer, B. \\
        2014, Astronomy \& Astrophysics, 571, A70. \\
        7 pp. --- 3 citations --- \href{http://adsabs.harvard.edu/abs/2014arXiv1405.7051F}{LINK}
    
	\item {\it BANYAN. IV. Fundamental Parameters of Low-Mass Star Candidates in Nearby Young Stellar Kinematic Groups---Isochronal Age Determination Using Magnetic Evolutionary Models} \\
      Malo, L.; Doyon, R.; {\bf Feiden, G.~A.}; Albert, L.; Lafreni\`{e}re, D.; Artigau, \'{E}.; Gagn\'{e}, J.; \& Riedel,~A. \\
      2014, The Astrophysical Journal, 792, 37. \\
      17 pp. --- 35 citations --- \href{http://adsabs.harvard.edu/abs/2014ApJ...792...37M}{LINK}
         
    \item  {\it Magnetic Inhibition of Convection and the Fundamental Properties of Low-Mass Stars. II. Fully Convective Main Sequence Stars} \\
       {\bf Feiden, G.~A.} \& Chaboyer, B. \\
       2014, The Astrophysical Journal, 787, 53. \\
       17 pp. --- 17 citations --- \href{http://adsabs.harvard.edu/abs/2014ApJ...789...53F}{LINK}
    
    \item {\it Characterizing the Cool KOIs. VI. H-- and K--Band Spectra of Kepler M Dwarf Planet-Candidate Hosts} \\
       Muirhead, P.~S.; Becker, J.; {\bf Feiden, G.~A.}; Rojas-Ayala, B.; Vanderburg, A.; Price, E.~M.; Thorp, R.; Law, N.~M.; Riddle, R.; Baranec, C.; Hamren, K.; Schlawin, E.; Covey, K.~R.; Johnson, J.~A.; Lloyd, J.~P. \\
       2014, The Astrophysical Journal Supplement, 213, 5. \\ 
       12 pp. --- 25 citations --- \href{http://adsabs.harvard.edu/abs/2014ApJS..213....5M}{LINK}

	\item[{\bf 2013}]

	\item {\it Magnetic Inhibition of Convection and the Fundamental Properties of Low-Mass Stars. I. Stars with a Radiative Core} \\
          {\bf Feiden, G.~A.} \& Chaboyer, B. \\
          2013, The Astrophysical Journal, 779, 183. \\
          25 pp. --- 42 citations --- \href{http://adsabs.harvard.edu/abs/2013ApJ...779..183F/}{LINK}

    \item {\it The Interior Structure Constants as an Age Diagnostic for Low-Mass, Pre-Main-Sequence Detached Eclipsing Binary Stars} \\
          {\bf Feiden, G.~A.} \& Dotter, A. \\
          2013, The Astrophysical Journal, 765, 86. \\
          7 pp. --- 2 citations --- \href{http://adsabs.harvard.edu/abs/2013ApJ...765...86F}{LINK}
          
    \item[{\bf 2012}]
    
    \item {\it Self-Consistent Magnetic Stellar Evolution Models of the Detached, Solar-Type Eclipsing Binary EF Aquarii} \\
          {\bf Feiden, G.~A.} \& Chaboyer, B. \\
          2012, The Astrophysical Journal, 761, 30. \\
          15 pp. --- 34 citations --- \href{http://adsabs.harvard.edu/abs/2012ApJ...761...30F}{LINK}
          
    \item {\it The Metallicity of the CM Draconis System} \\
          Terrien, R.~C.; Fleming, S.~W.; Mahadevan, S.; Deshpande, R.; {\bf Feiden, G.~A.}; Bender, C.~F.; \& Ramsey, L.~W. \\
          2012, The Astrophysical Journal Letters, 760, L9. \\ 
          6 pp. --- 17 citations --- \href{http://adsabs.harvard.edu/abs/2012ApJ...760L...9T}{LINK}
          
    \item {\it Age and helium content of the open cluster NGC 6791 from multiple eclipsing binary members II. age dependencies and new insights} \\
          Brogaard, K.; VandenBerg, D.~A.; Bruntt, H.;  Grundahl, F.; Frandsen, S.; Bedin, L.~R.; Milone, A.~P.; Dotter, A.; {\bf Feiden, G. A.}; Stetson, P.~B.; Sandquist, E.; Miglio, A.; Stello, D.; \& Jessen-Hansen, J. \\
          2012, Astronomy \& Astrophysics, 543, A106. \\
          17 pp. --- 65 citations --- \href{http://adsabs.harvard.edu/abs/2012A&A...380A.106B}{LINK}
          
    \item {\it Reevaluating the Mass-Radius Relation for Low-Mass, Main Sequence Stars} \\
          {\bf Feiden, G.~A.} \& Chaboyer, B. \\ 
          2012, The Astrophysical Journal, 757, 42. \\
          16 pp. --- 41 citations --- \href{http://adsabs.harvard.edu/abs/2012ApJ...757...42F}{LINK}
    
    \item[{\bf 2011}]
    
    \item {\it Accurate Low-Mass Stellar Models of KOI-126} \\
          {\bf Feiden, G.~A.}, Chaboyer, B., \& Dotter, A. \\
          2011, The Astrophysical Journal Letters, 739, L25. \\
          5 pp. --- 37 citations --- \href{http://adsabs.harvard.edu/abs/2011ApJ...740L..25F}{LINK}
          
    \item[{\bf 2007}]
    
    \item {\it Period-colour and amplitude-colour relations in classical Cepheid variables -- V. The Small Magellanic Cloud Cepheid models} \\
          Kanbur, S., Ngeow, C., \& {\bf Feiden, G.~A.} \\
          2007, Monthly Notices of the Royal Astronomical Society, 380, 819. \\ 
          9 pp. --- 7 citations --- \href{http://adsabs.harvard.edu/abs/2007MNRAS.380..819K}{LINK}

\end{etaremune}

\vspace{\baselineskip}

% Conference Proceedings, White papers, etc.
\noindent{\bf \large 2. Peer-reviewed conference contributions}

\begin{etaremune}[leftmargin=0.30in]
	\item \emph{Stellar Evolution Models of Young Stars: Progress and Limitations} \\
	{\bf Feiden, G.~A.} \\
	2016, ``Young Stars and Planets Near the Sun,'' IAU Symposium, 314. \\
	6 pp. --- 1 citation --- \href{http://adsabs.harvard.edu/abs/2015IAUS..314...79F}{LINK}

	\item \emph{Pilot Study: Assessing Student Perception of the Collaborative Annotation Platform
	{\rm Open Rev} in a Classroom Environment} \\
	{\bf Feiden, G.~A.} \\
	2015, on Authorea, review in Academic Teacher Training at Uppsala University. \\
	9 pp. --- \href{https://www.authorea.com/users/18170/articles/20333/}{LINK}

	\item \emph{Eclipsing Binaries as Tests of Low--Mass Stellar Evolution Theory} \\
	{\bf Feiden, G.~A.} 
	2015, ``Living Together: Planets, Host Stars, and Binaries,'' PASP Conference Series, 496, 137 -- 151. \\
	15 pp. --- 1 citation --- \href{http://adsabs.harvard.edu/abs/2015ASPC..496..137F}{LINK}
	
	\item \emph{The Benchmark Eclipsing Binary V530 Ori: A Critical Test of Magnetic Evolution 
	            Models for Low--Mass Stars} \\
	Torres, G.; Lacy, C.~H.~S.; Pavlovski, K.; {\bf Feiden, G.~A.}; Sabby, J.~A.; Bruntt, H.; \& Clausen, J.~V. \\
	2015 ``Living Together: Planets, Host Stars, and Binaries,'' PASP Conference Series, 496, 169 -- 173. \\
	5 pp. --- 1 citation --- \href{http://adsabs.harvard.edu/abs/2015ASPC..496..169T}{LINK}
	
	\item \emph{Spectroscopic Study of the Low-Mass Benchmark Eclipsing Binary UV Piscium} \\
	{\bf Feiden, G.~A.}; Stempels, H.~C.; Hebb, L.; Mack, C. E., III; \& Chaboyer, B. \\
	2015, ``Living Together: Planets, Host Stars, and Binaries,'' PASP Conference Series, 496, 174. \\
	1 pp. --- \href{http://adsabs.harvard.edu/abs/2015ASPC..496..174F}{LINK}
	
	\item \emph{Touchstone Stars: Highlights from the Cool Stars 18 Splinter Session} \\
	 Mann, A.~W.; Kraus, A.; Boyajian, T.~S.; Gaidos, E.; von Braun, K.; {\bf Feiden, G.~A.}; Metcalfe, T.; Swift, J.~J.; Curtis, J.~L.; Deacon, N.~R.; Filippazzo, J.~C.; Gillen, E.; Hejazi, N.; \& Newton,~E.~R. \\
	 2015, in proceedings of ``The 18th Cambridge Workshop on Cool Stars, Stellar Systems, and the Sun,'' 80 -- 104. \\
	 25 pp. --- 1 citation --- \href{http://adsabs.harvard.edu/abs/2015csss...18..171F}{LINK}

	\item \emph{Updating the Dartmouth Stellar Evolution Model Grid: Pre-Main-Sequence Models \& Magnetic Fields} \\
	{\bf Feiden, G.~A.}; Jones, J.;$^{\dagger}$ \& Chaboyer, B. \\
	2015, ``The 18th Cambridge Workshop on Cool Stars, Stellar Systems, and the Sun,'' 171 -- 176. \\
	3 pp. --- 3 citations --- \href{http://adsabs.harvard.edu/abs/2015csss...18...80M}{LINK}
	
	\item \emph{Prospects for the BANYAN search of low-mass moving group members with Gaia, and the importance of magnetic fields for isochrone age determination} \\
		Malo, L.; Gagne, J.; Doyon, R.; Lafreniere, D.; Artigau, E.; {\bf Feiden, G.~A.}; \& Albert, L. \\
		2014, ``{\it Gaia} and the Unseen. The Brown Dwarf Question,'' MmSAI, 85, 715. \\
		4 pp. --- \href{http://adsabs.harvard.edu/abs/2014MmSAI..85..715M}{LINK}
		
	\item \emph{Do Magnetic Fields Actually Inflate Low-Mass Stars?} \\
    {\bf Feiden, G.~A.} \& Chaboyer, B. \\
    2014, ``Magnetic Fields Throughout Stellar Evolution,'' IAU Symposium, 302, 150. \\
    4 pp. --- 1 citation --- \href{http://adsabs.harvard.edu/abs/2014IAUS..302..150F}{LINK}

    \item \emph{Magnetic Field Induced Radius Inflation of Low-Mass Stars} \\ 
    {\bf Feiden, G.~A.} \& Chaboyer, B. \\
    2013, ``Setting a new standard in the analysis of binary stars,'' EAS Publication Series, 64, 127. \\
    4 pp. --- \href{http://adsabs.harvard.edu/abs/2013EAS....64..127F/}{LINK}
    
    \item \emph{Parallaxes of metal-poor main-sequence stars} \\
    Chaboyer, B.; {\bf Feiden, G.~A.}; Benedict, G.~F.; McArthur, B.~E.; Harrison, T.~E.; McWilliam, A.; Nelan, E.~P.; Patterson, R.~J.; \& Sarajedini, A. \\
    2013, ``Advancing the Physics of Cosmic Distances,'' IAU Symposium, 289, 87. \\
    4 pp. --- \href{http://adsabs.harvard.edu/abs/2013IAUS..289...87C}{LINK}
\end{etaremune}

\vspace{\baselineskip}

\noindent{\bf \large 3.\ Monographs}
\begin{etaremune}[leftmargin=0.30in]
	\item \emph{Dartmouth Magnetic Evolutionary Stellar Tracks and Relations} \\
		{\bf Feiden, G.~A.} \\
		2013, ProQuest, ISBN 9781303770432. \\
		343 pp. --- 2 citations --- \href{http://adsabs.harvard.edu/abs/2013PhDT.......149F}{LINK}
\end{etaremune}

\vspace{\baselineskip}

\noindent{\bf \large 4.\ Research review articles}

\begin{etaremune}[leftmargin=0.30in]
	\item \emph{Pre-Main-Sequence Stellar Structure and Evolution} \\
		{\bf Feiden, G.~A.} \\
		Commissioned in Feb 2016, Publications of the Astronomical Society of the Pacific. 
		
	\item {\it Empirical Tests of Pre--Main--Sequence Stellar Evolution Models with Young Eclipsing Binary~Stars} \\
          Stassun, K.~G.; {\bf Feiden, G.~A.}; \& Torres, G. \\
          2014, New Astronomy Reviews, 60, 1. \\
          28 pp. --- 14 citations --- \href{http://adsabs.harvard.edu/abs/2014NewAR..60....1S}{LINK}
\end{etaremune}

%\noindent{\bf \large Other academic works}
%
%\begin{etaremune}[leftmargin=0.30in]
%
%	\item Open Research Notebook (\href{https://github.com/gfeiden/Notebook/}{GitHub})
%	
%	\item \texttt{k2age}: software to compute ages of binary stars using stellar internal structure constants. Based on Feiden \& Dotter (2013, ApJ, 765, 86; \href{https://github.com/gfeiden/k2age}{GitHub})
%\end{etaremune}

\vspace{\baselineskip}

\begin{flushright}
	\emph{\footnotesize compiled on: \today}
\end{flushright}

\end{document}
